Argennon: A Scalable Cloud Based Smart Contract Platform Using Argument of Knowledge Systems

### 2022-08-21 tex/sections/intro.tex
Mention arithmetiztion in the intro
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

Argennon applications (i.e smart contracts) are stored in a high level text based language on the blockchain. This
language is intended for preserving the
high level information of the application logic to facilitate platform specific compiler optimization at a host
machine. This enables delegates to compile and optimize Argennon applications for their specific hardware platforms
and execute applications efficiently, ensuring the state transition can be found as fast as possible.

@@

Using Succinct Argument of Knowledge systems makes the main functionalities of an Argennon validator light enough to
be implemented as a smart contract. By deploying a validator contract on another platform, Argennon
could use more established blockchains as an extra layer of security, specially
during the bootstrapping phase, when ARG is not well distributed yet. In addition, this contract will facilitate
trustless bridging of assets to the Argennon blockchain. To reduce the execution fee, this validator
contract can be used for validating only roll-ups of the state transition.

>>>>

Argennon applications (i.e smart contracts) are stored in a high level text based language on the blockchain. This
language is intended for preserving the
high level information of the application logic to facilitate platform specific compiler optimization at a host
machine. This enables delegates to compile and optimize Argennon applications for their specific hardware platforms
and execute applications efficiently, ensuring the state transition can be found as fast as possible. Moreover,
validators by using a special compiler, generate arithmetization of this language and use it for verifying CI proofs.

@@

Using Succinct Argument of Knowledge systems makes the main functionalities of an Argennon validator light enough to
be implemented as a smart contract. By deploying a validator contract on another platform, Argennon
could use more established blockchains as an extra layer of security, specially
during the bootstrapping phase, when ARG is not well distributed yet. In addition, this contract will facilitate
trustless bridging of assets from that platform to the Argennon blockchain. To reduce the execution fee, only
roll-ups of the state transition can be validated by the contract.
